---
title: "dashboard for european reserves of gold"
author: "alexis carbillet"
date: "14 janvier 2020"
output: html_document
params:
  country:
    value: any
    choices:
      - Austria
      - Belgium
      - Bulgaria
      - Croatia
      - Cyprus
      - Czech Republic
      - Denmark
      - Estonia
      - Finland
      - France
      - Germany
      - Greece
      - Hungary
      - Ireland
      - Italy
      - Latvia
      - Lithuania
      - Luxembourg
      - Malta
      - Netherlands
      - Poland
      - Portugal
      - Romania
      - Slovakia
      - Slovenia
      - Spain
      - Sweden
      - United Kingdom
      
  year:
    input: slider
    min: 2003
    max: 2014
    step: 1
    round: 1
    sep: ''
    value: 
    - 2006
    - 2010
---
```{r setup,echo=FALSE,warning=FALSE, message=FALSE}
library(magrittr)
countryName <- params$country
startYear <- params$year[1]
endYear <- params$year[2]
if (countryName == "any") { countryName <- "" }
```

This project use the european reserves by country dataset. This dataset has been already used in the past, you can find its description in this link: <a href="https://alexiscarbillet.github.io/Visualization-Project/" target="_blank">Gold Reserves (website in French)</a>.

When you run the R code, a first window is created. It contains a list of country and a slider. So it is possible to choose the country and the temporal interval. Many studies are possible. In total, 28 countries are available.

The whole project can be found in my <a href="https://alexiscarbillet.github.io/dashboard/" target="_blank">github repository</a>. You can also reach my <a href="https://www.alexis-carbillet.eu/" target="_blank">personnal website</a> if you need to contact me or to discover the other projects I worked on.

```{r echo=FALSE,warning=FALSE, message=FALSE}
# take the data from the excel
library(readxl)
data <- read_excel("C:/Users/alexis/Desktop/projet perso/european-reserves-by-country.xls")
```

```{r echo=FALSE,warning=FALSE,  message=FALSE}
colnames(data) <- NULL
countries <- c("Austria", "Belgium", "Bulgaria", "Croatia",  "Cyprus", "Czech Republic", "Denmark", "Estonia","Finland", "France", "Germany", "Greece",  "Hungary", "Ireland", "Italy", "Latvia", "Lithuania", "Luxembourg", "Malta", "Netherlands", "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", "Sweden","United Kingdom")
z <- which(match(countries,countryName)==1)
dataset <- data[(2+5*(z-1)):(5*z)]
dataset <- dataset[3:59,1:4]
names(dataset)=c("tonnes gold", "$ gold", "$ FX", "$ total")
```
Below, you can find an interactive graphic which represent the evolution of the quantity of gold, the value of the gold in \$, the FX in \$ and the total value of the gold reserve of the country studied (in \$ too). You chose to study `r countryName` which is a beautiful country. In the bottom of the graphic, there is a temporal window. It allows to change the beginning and the end of the interval time.
```{r echo = FALSE, fig.width=8, fig.height=4,warning=FALSE,message=FALSE}
library(zoo)
window <- c( yearqtr(startYear), yearqtr(endYear))

dygraphs::dygraph(ts (dataset, start=c(2003), end=c(2014), frequency=4), main = "reserves of this country in tonnes of gold") %>% 
  dygraphs::dyAxis("y", axisLabelWidth = 30) %>%
  dygraphs::dyOptions(drawPoints = TRUE, pointSize = 2) %>%
  dygraphs::dyRangeSelector(dateWindow = window)
```
This first graphic use the library dygraphs. This one provides rich facilities for charting time-series data in R, including:

- Automatically plots xts time series objects (or any object convertible to xts).

- Highly configurable axis and series display (including optional second Y-axis).

- Rich interactive features including zoom/pan and series/point highlighting.

- Display upper/lower bars (e.g. prediction intervals) around series.

- Various graph overlays including shaded regions, event lines, and point annotations.

- Use at the R console just like conventional R plots (via RStudio Viewer).

- Seamless embedding within R Markdown documents and Shiny web applications.

In this part, a choropleth map has been drawn. In red are the different countries that ca be selected during the first step. In yellow is represented the one selected.

```{r echo = FALSE, fig.width=10, fig.height=8, warning=FALSE, message=FALSE}
library(ggplot2)
library(grid)
library(rworldmap)

worldMap <- getMap()
countrie <- c("Austria", "Belgium", "Bulgaria", "Croatia",  "Cyprus", "Czech Rep.", "Denmark", "Estonia","Finland", "France", "Germany", "Greece",  "Hungary", "Ireland", "Italy", "Latvia", "Lithuania", "Luxembourg", "Malta", "Netherlands", "Poland", "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", "Sweden","United Kingdom")
indEU <- which(worldMap$NAME%in%countrie)

europeCoords <- lapply(indEU, function(i){
  df <- data.frame(worldMap@polygons[[i]]@Polygons[[1]]@coords)
  df$region =as.character(worldMap$NAME[i])
  colnames(df) <- list("long", "lat", "region")
  return(df)
})

europeCoords <- do.call("rbind", europeCoords)

value <- sample(x = c(0), size = length(countries), replace = TRUE)
value[z] = 1
europeanUnionTable <- data.frame(country = countrie, value = value)
europeCoords$value <- europeanUnionTable$value[match(europeCoords$region,europeanUnionTable$country)]

P <- ggplot() + geom_polygon(data = europeCoords, aes(x = long, y = lat, group = region, fill = value),colour = "black", size = 0.1) 

P <- P + scale_fill_gradient(name = "Country selected", low = "#FF0000FF", high = "#FFFF00FF", na.value = "grey50")

P <- P + theme(axis.text.x = element_blank(),
               axis.text.y = element_blank(), axis.ticks.x = element_blank(),
               axis.ticks.y = element_blank(), axis.title = element_blank(),
               plot.margin = NULL)
P
```